This study presented a rigorous experimental characterization of BS effects on ranging estimation for UWB systems operating in the 6.5 GHz band, addressing a critical gap in empirical data for this frequency. The following core conclusions are drawn:

\begin{enumerate}
    \item \textbf{Optimal Tag Placement Hierarchy:} The physical placement of the wearable node is the single most dominant factor determining system reliability under NLOS conditions. The head placement unequivocally emerged as the optimal placement, retaining sub-decimeter accuracy in most scenarios by effectively leveraging cranial signal diffraction. Conversely, placing the tag on the torso (i.e., chest or hip) generates catastrophic degradation (i.e., MAE exceeding 95 cm under NLOS conditions). This establishes a fundamental design constraint for safety-critical systems: reliance on belt-mounted tags introduces unacceptable error risks without sophisticated auxiliary compensation algorithms.

    \item \textbf{Frequency-Specific Propagation and Constructive Multipath:} It was empirically identified and shown that the existence of the "Constructive Multipath" paradox in the 6.5 GHz band. For highly mobile extremities (i.e., the wrist, hand, or knee), the confined indoor environment acts as a spatial "diversity provider," generating multi-path reflections that successfully circumvent direct body blockage. As a result, NLOS ranging errors are significantly and systematically lower in cluttered indoor corridors than in open outdoor fields. This discovery shows that environmental reflections can be deliberately exploited in indoor network planning to mitigate BS.

    \item \textbf{Statistical Error Modeling and the Failure of Gaussian Assumptions:} It was mathematically shown that the fundamental assumption of Gaussian noise is entirely invalid for human tracking under obstructed UWB conditions. By fitting theoretical distributions to over 100,000 independent samples, it was shown that ranging errors undergo a structural transformation: from a relatively symmetric gamma distribution under LOS to a severely skewed, heavy-tailed Log-normal distribution under BS. Consequently, traditional positioning filters (such as standard Kalman Filters or Least Squares multilateration) that rely on zero-mean Gaussian assumptions are theoretically incapable of correcting the massive systematic positive bias induced by the BS.
\end{enumerate}

These findings establish a definitive empirical baseline for the development of future, high-precision industrial tracking solutions. To overcome the inherent physical limitations imposed by the BS, future research must shift from traditional linear filtering techniques to dynamic, "distribution-aware" architectures. The next generation of robust positioning systems will require algorithms that perform real-time diagnostic checks on UWB link quality and dynamically transition between a Gamma observation model (in LOS) and a Log-normal bias-compensation model (in NLOS), thereby directly addressing the limitations mathematically characterized in this work.
